\documentclass[]{rss}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{
            pdftitle={Resume},
            colorlinks=true,
            linkcolor=blue,
            citecolor=Blue,
            urlcolor=Blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother


\date{}

\begin{document}

\name{Lukasz Tymoszczuk}
\address{\\[-9pt] lukas@codeily.com | lukastymo.com}
\begin{resume}

I'm a Scala / Data Engineer with over ten years' experience. I inspire
and help teams in being productive. I love mathematics and algorithms.

I'm goal oriented, proactive and able to work remotely, with outstanding
communications skills.

My business domain: Machine Learning (2018), Finance, Risk Management
FRTB, MIFID, Basel: 5 years (2008 - 2010, 2013 - 2015, 2018), Energy
industry: Energy price forecasting (2017), Public sector: Automatic
recruitment (2016), Airline (2010 - 2013).

Info:

\begin{itemize}
\tightlist
\item
  \href{https://github.com/lukastymo}{\texttt{github.com/lukastymo}}
\item
  \href{https://stackoverflow.com/users/574799/smas}{\texttt{stackoverflow.com/users/574799/smas}}
  (top 2\%)
\item
  \href{https://codeforces.com/profile/smas}{\texttt{codeforces.com/profile/smas}}
\end{itemize}

Technical experience:

\begin{itemize}
\tightlist
\item
  Scala, Functional Programming, Java, JVM
\item
  Agile Development practices: CI/CD, TDD, PP, Code Review
\item
  Machine Learning, Python / Jupyter Notebook
\item
  Big Data: Apache Spark (development and tuning), ETL, SQL
\item
  Distributed Systems: Akka, Microservices, NoSQL, The Twelve-Factor App
\item
  DevOps \& Cloud: AWS, Google Cloud Platform, Azure, Ansible,
  Terraform, Docker and Kubernetese, ELK
\end{itemize}

\subsubsection{Data Engineer (contract)}\label{data-engineer-contract}

\emph{Royal Mail \textbar{} GBI} May 2018 -- Present, London, UK

\begin{itemize}
\item
  I was part of Data Engineering team. I developed Data Platform and
  data algorithms on it which transformed the whole business and allowed
  releasing multiple great products. I advised and recommended best
  practices in Scala, Agile and Software Development, Architecture.
\item
  I implemented opt-1, opt-2 and opt-3 heuristic to solve VRP (Vehicle
  routing problem). This algorithm was essential for Royal Mail
  business, as it is unpractical to solve this task manually. Thanks to
  this algorithm another project ``Late Arrival Packages'' was able to
  kick off.
\item
  I developed parcel delivery project which processed terabytes of data
  in a few hours. I was responsible for productionizing (porting from
  POC Python code to Scala) and implemented new features for Machine
  Learning modules: Train, Test, Post-process and Formatter. This
  project was able to predict 90\% of all packages UK-wide with 2-hour
  precision.
\end{itemize}

Tech stack:

\begin{itemize}
\tightlist
\item
  Scala, Apache Spark, Spark SQL, Yarn, HDFS, Linux, Apache Zeppelin,
  Python, TDD
\item
  Kubernetes, Docker, Akka-HTTP, MongoDB, Cats
\item
  On-premise Cloud
\item
  REST, swagger, gatling, postman
\end{itemize}

\subsubsection{Big Data Developer
(contract)}\label{big-data-developer-contract}

\emph{IHS Markit \textbar{} Risk Factor Utility (FRTB)} September 2017
-- May 2018, London, UK

\begin{itemize}
\item
  I was part of the team which implemented very popular, and in-demand
  project required transforming significant amount of raw market data
  into FRTB-compliant risk factors and scenarios by using DSL language
  for risk modelling.
\item
  I productionized Spark application on AWS (S3, EC2, EMR) with strong
  automatization requirement via Ansible and CloudFormation. Due to this
  change deployment across environments was consistent and automated so
  everybody on the team could do this by clicking one button in Jenkins.
\item
  I helped developing functional Scala project, which the main module
  was a custom DSL language used by Quants. Thanks to this feature our
  quants were able to produce FRTB solutions presented for multiple
  banks.
\end{itemize}

Tech stack:

\begin{itemize}
\tightlist
\item
  TDD, Code review, Scrum team
\item
  Scala + cats library, Monix, Low-level Scala for DSL creation:
  Reflection, Sandbox
\item
  REST and Swagger
\item
  Apache Spark, Hadoop, Cassandra
\item
  AWS (EC2, S3), Cloud Computing, EMR, Yarn
\item
  Apache Zeppelin, Big Data, Helping BAs with notebooks written in
  Python
\item
  Agile: Scrum
\item
  CI / CD, Ansible, Git workflow
\end{itemize}

\subsubsection{Software Engineer
(contract)}\label{software-engineer-contract}

\emph{OVO Energy \textbar{} vCharge} April 2017 -- September 2017,
London, UK

\begin{itemize}
\item
  vCharge was a startup acquired by Ovo Energy. The idea was to control
  storage heaters installed in people homes. I worked with the owner who
  was located in the US (\textasciitilde{} daily one-to-one online
  meetings). I had a high impact on stakeholders. Throughout a couple of
  months, I was the only Scala developer.
\item
  I built a module to forecasting Energy prices using the Dijkstra
  algorithm and mathematical model created by Data Scientists. It
  allowed buying energy cheaper and ``store'' in the customers' storage
  heaters.
\end{itemize}

Tech Stack:

\begin{itemize}
\tightlist
\item
  Scala, Akka, Play Framework, Lagom Framework
\item
  Python, C++
\item
  CQRS / Event Sourcing, Cassandra
\item
  Microservices
\item
  ScalaTest, Property-based testing
\end{itemize}

\subsubsection{Scala Consultant
(contract)}\label{scala-consultant-contract}

\emph{Civil Service Resourcing (Valtech) \textbar{} Faststream,
Fasttrack} February 2016 -- April 2017, London, UK

\begin{itemize}
\tightlist
\item
  I developed an auto-grader module inside the web-based application
  deployed on HMRC's Tax Platform. The module allowed to assess and send
  emails to 120,000 candidates in a day-scale vs month-scale in the
  legacy system.
\end{itemize}

Tech stack:

\begin{itemize}
\tightlist
\item
  Scala and functional design
\item
  Play framework, RESTful API, MongoDB
\item
  Microservices, Kibana, Grafana
\item
  Cucumber, ScalaTest, Property-based testing
\end{itemize}

\subsubsection{Senior Software Engineer}\label{senior-software-engineer}

\emph{Monitise \textbar{} FinKit platform, Matm} August 2013 -- February
2016, London, UK

\begin{itemize}
\tightlist
\item
  After a year of developing OSGI, Java platform for multiple financial
  institutions I was moved to brand new cloud platform with Scala, Akka,
  Microservice architectures: FinKit.
\end{itemize}

Tech stack:

\begin{itemize}
\tightlist
\item
  Scala, Akka
\item
  REST: Spray, Swagger (generator)
\item
  IBM Bluemix, NoSQL: Cloudant, AMQP protocol
\item
  Java 6 / 7, Apache Camel
\item
  Modularization: OSGi, Messaging: JMS
\item
  REST, SOAP, SOA
\item
  TDD, BDD, Continuous Delivery, Continuous Integration
\end{itemize}

\subsubsection{Full stack Java
Developer}\label{full-stack-java-developer}

\emph{Sabre Holdings} November 2010 -- August 2013, Krakow, Poland

\begin{itemize}
\item
  I helped in developing web-based, highly configurable booking
  application for numerous airlines.
\item
  I proposed and implemented speeding up development by recording a web
  state to disk. A tester could persist the current state of the
  application, and a developer could retrieve it at any time, at any
  moment -- saving time and reproducing some nasty bugs in a second.
\end{itemize}

Tech stack:

\begin{itemize}
\tightlist
\item
  Java 5 / 6
\item
  Spring Core, MVC, Webflow
\item
  JavaScript, JSP
\item
  TDD, Continuous Integration, Object-Oriented Programming, SOLID
\end{itemize}

\subsubsection{Full stack Java
Developer}\label{full-stack-java-developer-1}

\emph{ComArch} June 2008 -- November 2010, Krakow, Poland

Tech stack:

\begin{itemize}
\tightlist
\item
  Research: Comparing AJAX JSF frameworks: ICEfaces vs RichFaces
\item
  Tomcat \& Websphere
\item
  Java 5 / 6, JSF, Portlets, JavaScript, AJAX
\end{itemize}

\subsubsection{Education}\label{education}

M.S., Computer Science, Jagiellonian University, 2005 - 2010, Krakow,
Poland

\begin{itemize}
\tightlist
\item
  Diploma dissertation: Comparing JSF frameworks: ICEfaces and RichFaces
\end{itemize}

\subsubsection{Projects}\label{projects}

\begin{itemize}
\tightlist
\item
  \href{https://appointary.com}{\texttt{appointary.com}}
\item
  \href{http://stepstoyourhome.co.uk}{\texttt{stepstoyourhome.co.uk}}
\item
  \href{http://www.lukastymo.com/inc/blog}{\texttt{www.lukastymo.com/inc/blog}}
\end{itemize}

\end{resume}

\end{document}
